A meta-analysis of the impacts of best management practices on nonpoint source pollutant concentration.

### 2024-05-30 frontiers_submission/reviewer_response/reviewer_response.qmd

---
title: "Response to reviewer comments"
format:
  hikmah-response-typst: default

bibliography: biblio.bib
---

@@

::: {.memo-excerpt}
A few reviews have noted a common trend of insufficient methodological and site specific data among peer-reviewed BMP performance studies (Grudzinski et al., 2020; Eagle et al., 2017; Liu et al., 2017). We confirm that inconsistent reporting among studies complicates data extraction, effect size calculations, and attributing important sources of variance. Our desire to evaluate the effects of specific BMP parameters was hinderd by the overall lack of reporting of relevant parameters such as drainage area, infiltration media/soil, infiltration volume, riparian/buffer width and area, and other relevant factors. The lack of BMP specific parameters certainly contributes to our relatively high model variance. The International Stormwater BMP Database addresses some of these concerns through a standardized reporting format. Our future efforts will incorporate data from the International Stormwater BMP Database with data retrieved through a systematic review. Additionally, this study was a broad scale look across BMP types which limits factors that cannot be compared across different types of BMPs. For example, livestock management BMPs may not rely on or report parameters such as vegetative buffer width or infiltration area. Inclusion of such factors in our meta-regression approach would necessarily exclude certain types of BMPs. Future BMP-specific meta-analysis might be more useful and informative for practitioners by providing effect sizes of parameters that were necessarily excluded from our study.
:::

---

::: {.memo-reviewer}
***Reviewer 2***: The heterogeneity of FIB, TN, TP, TSS are high, the study 
require subgroup analysis or sensitivity analysis on this issue.
:::

I appreciate this comment, but want to caution against extensive subgroup 
analysis/sensitivity analysis. While heterogeneity was indeed high, 
the primary purpose of the meta-regression models are to investigate how much
of the variance that a set of pre-determined moderators explain. Meta-regression
were conducted in lieu of traditional subgroup analysis. While additional 
subgroup analysis could be conducted based on additional moderators, we risk 
conducting a "data-dredging" study [@thompsonHowShouldMeta2002]. However, we did add post-hoc sensitivity analysis for runoff source and catchment scale to the paper based on this suggestion. 
We did not find strong evidence indicating these factors are highly
influential to the results we found. This is likely, as you correctly point out,
do to the lack of BMP specific parameters that better explain performance than our chosen moderators.

@@

# Reviewer 3

::: {.memo-reviewer}
***Reviewer 3***: Is there any moderating effects of study area size or scale (i.e., field, farm, and watershed) and urban versus agricultural source on the performance of BMPs?
:::

We added an additional post-hoc sensitivity analysis for both these factors to the study. While this is not the same as fully incorporating the moderators into the original model, the sensitivity analysis indicates that we don't have strong evidence that these terms are highly influential to our results. This is confounded in part by the fact some of our BMP types are only applied to urban or agricultural BMPs and highlights a need for future meta-analysis to be applied for specific BMP types instead of across multiple BMP types.

@@

::: {.memo-excerpt}
Study locations were recrorded as latitude and longitude coordinates as described in studies.
If coordinates were not provided, the study team used Google Maps to locate approximate study location using site descriptions (county, city, municipal buildings, etc.) from the study and recorded the coordinates.
:::

---

::: {.memo-reviewer}
***Reviewer 3***:  Have you examined the effects of soil biophysical properties in addition to aridity? Can you obtain more detailed spatial locations of the various studies so to link these studies to local soil conditions in addition to climate?
:::

We did not include soil properties with the assumption that many infiltration based BMP modify soil as part of BMP construction. It is certainly possible that native soil conditions provide some additional moderating effect, but we did not obtain this data based on our assumptions.

@@

---

::: {.memo-reviewer}
***Reviewer 3***:  Could you please elaborate more on the topic “scaling BMP pollutant reductions to basin wide water quality improvement remains a substantial challenge”. This is a very interesting point, what modeling or mixed approaches exist to achieve this goal?
:::

We have expanded on this slightly in the conclusion. Essentially it is difficult to empirically link water quality improvements to BMP implementation in many studies due to short study lengths, underlying measurement and analytic uncertainty, and difficulty establishing adequate controls. Many watershed scale studies therefore rely on numeric watershed models to demonstrate BMP performance (see the USDA CEAP program for example).

@@

Fixed.

# Reviewer 4

::: {.memo-reviewer}
The statistical analysis was rigorous and thorough. That, alone, warrants a recommendation for acceptance of this manuscript. My primary concern is that the models were fitted using only one of the four BMP variables – BMP Subcategory. Were models with the other three BMP variables evaluated? In the mid-Atlantic US region, critically important BMPs for rural and agricultural lands are vegetative buffer strips, and for urban areas constructed wetlands are quite important. For example, much work has been done by researchers in North Carolina on metrics of vegetative buffer strips related to their effectiveness. Evaluation of models with specific practice characterization would have been informative. 
:::

We agree with the overall comment here. This paper was our first cut analysis across a broad range of BMPs. Our approach requires somewhat broad variables used in the regression models so we do not eliminate studies that do not include specific BMP data, such as buffer strip width. Further meta-analysis should focus on specific practices where relevant specific BMP parameters can be properly evaluated. We've added additional context in the Study Limitations section.

@@

---

::: {.memo-reviewer}
That leads me to my second concern. Only the last paragraph of the manuscript is presented as a summary. I recommend that this paragraph be reconstituted as a separate “Conclusion” section and that it be more thorough than this simple summary paragraph. For example, it would be useful to know what the authors expected to find in their modeling studies versus what actually was found. 
:::

We have incorporated a conclusions section and expanded a bit more on our expectations as well as incorporated suggestions from other reviewers.

@@

Added.

---

::: {.memo-reviewer}
***Reviewer 5***:   1st Paragraph of introduction (Line 28), add a sentence about sediment impairments to waters similar to the ones discussing FIBs and nutrients impairments
:::

Added the following:

::: {.memo-excerpt}
Approximately 15% of river and streams have excessive sedimentation, which leads to twice the likelihood of a stream to have poor biological condition (EPA, 2017).
:::

@@

---

::: {.memo-reviewer}
***Reviewer 5***:   Include small paragraph in discussion about how search terms of “BMPs” or “best management practices” and inclusion criteria (concentrations) may have not captured some studies. For example, if the study used the name of the practice instead of BMP. Also, there are a suite of agricultural drainage practices but studies generally focus on load reduction (from flow reduction) compared to concentration reduction (see Frankenberger et al., 2023 https://elibrary.asabe.org/abstract.asp?aid=54314 who’s review has a cluster of those studies in the Midwest, which is blank on this map). 
:::

This escaped our notice, thanks for raising this relevant shortcoming. We added the following to the Study Limitations section within the discussion:

::: {.memo-excerpt}
One reviewer also noted some examples of missing studies, attributable to our selection of search terms and inclusion criteria (Table 1). In particular, our search query did not include specifc practice names, instead using “BMP” or “best management practice” as a keyword search. This choice may have led us to miss studies that only included the practice name. Or inclusion criteria of concentration based studies may have also lead to the exclusion of studies that focused on load reductions (through flow reductions) but may have included data on relevant concentration effects.
:::

@@

---

::: {.memo-reviewer}
***Reviewer 5***:   Lines 61 – 64 consider adding an example BMP for instances where effluent is and is not related to influent concentration
:::

We modified the lines to include the following:

::: {.memo-excerpt}
Barrett (2005) demonstrated
that percent pollutant reduction is often a function of influent quality. Specifically, for certain types of BMPs
percent removal is low at low influent concentrations, and increases with increasing influent concentrations.
Horvath et al. (2023) found that influent phosphorus concentrations had some explanatory ability for
BMP performance among grass strips, bioretnetion, and grass swale BMPs. However, for some types
of BMPs, such as media filters and permanently pooled retention basins (Barrett, 2005) and pollutant
parameters, effluent concentration is unrelated to influent concentration. 
:::

@@

Fixed.

---

::: {.memo-reviewer}
***Reviewer 5***:   Lines 213 – 214 – clarify “may not be reliable” in general, or just for lower aridity?
:::

It would not be reliable when extrapolated to lower aridity regions due to lack of model coverage. Clarified this in text.

@@

Added.

---

::: {.memo-reviewer}
***Reviewer 5***:   Lines 242-254: Nice discussion on spatial coverage with the caveat that we are not aware of the actual distribution of BMPs. However, I am curious, are BMPs over-represented or just predominately located in humid regions? Could it be related to larger population concentrations along the humid east coast than the arid west? Are detention practices common in locations with little rainfall and high potential loss of water to evaporation? See my recommendation for Figure 7 to potentially add a 3rd distribution of aridity index of urban & agricultural land covers across the US. 
:::

We have added a third distribution, based on your suggestion below, looking at just urban and agricultural land and still find some discrepancies in the distribution of aridity values.

@@

---

::: {.memo-reviewer}
***Reviewer 5***:  Lines 349 – 351: Based on your experience trying to synthesis information across studies in this review process, do you have recommendations for minimum reporting requirements or standards for future studies on BMP concentration reductions? If so, please list in text or perhaps in a box. 
:::

We added the following text to the conclusions:

::: {.memo-excerpt}
To improve future data synthesis efforts, we highly reccomend future BMP studies
follow the reporting guidelines provided in Eagle et al. (2017). In particular provide clearly defined water
quality parameters, tabular data (either in the manuscript, as supplemental material, or in an open data
repository), and error estimation at minimum. Control and treatment means should be made available in
reports, not just the transformed efficiency or percent change values. Furthermore clearly defined controls
and treatments are fundamental for comparing across studies. Finally, a major shortcoming in our synthesis
was driven by the lack of reported covariate data. Although data such as soil type may not be an within
study experimental covariate, documenting of these types of study variables is useful for data synthesis
efforts.
:::
---

### 2024-05-30 frontiers_submission/frontiers_submission.Rmd
prep for resubmission

## this sets our default code chunk options
knitr::opts_chunk$set(dev = "ragg_png",
                      echo = FALSE,
                      ## figure chunk options
                      fig.cap = TRUE,
                      fig.width = 6,
                      dpi = 300)

@@

Our systematic review identified a total of 33 studies and 125 effect sizes on FIB, 24 studies and 50 effect sizes on TN, 31 studies and 88 effect sizes for DIN, 31 studies and 61 effect sizes for TP, 17 studies and 36 effect sizes for PO~4~, and 33 studies with 125 effect sizes for TSS. 
The majority of studies were identified as smaller scaled lot or field studies (Figure \@ref(fig:bmpsummary) A).
FIB studies had a roughly equal proportion of large watershed/catchment studies and studies conducted at the community/farm scale or smaller.
We also identified that the majority of studies (all parameters) were conducted on urban or non-agricultural runoff (Figure \@ref(fig:bmpsummary) B).
We did identify a wide variety of BMPs in the review, but it did not appear that any particular type of BMP was responsible for the majority of studies for any given parameter (Figure \@ref(fig:bmpsummary) C).
Our review was restricted to studies published after between 1999 and 2023.
The number of studies published for each parameter were roughly uniformly distributed over time (Figure \@ref(fig:bmptemporal) A) and are not indicative of increases or decreases in the number of published studies.
Study length was strongly skewed for all parameters (Figure \@ref(fig:bmptemporal) B). Median study lengths were 3 (DIN), 2 (FIB), 2.5 (PO~4), 2.5 (TN), 2.5 (TP), and 2 (TSS) years. 
There appears to be a strong clustering of BMP studies in the mid-Atlantic region (North Carolina, Virginia, Maryland) with other states sparsely represented or completely absent from the review (Figure \@ref(fig:studymap)).

@@

There were only 19 studies and 63 FIB effect sizes available to model after removal of studies and effects that only reported BMP~eff~.
The overall mean effect (estimated with the intercept only multilevel random effects model) showed significant mean reductions in FIB (ROM = 0.85, 95% CI [0.36, 1.34]; BMP~eff~ = 57.4%, 95% CI [30.4%, 73.9%]; Figure \@ref(fig:overalleffect)) resulting from BMPs. 
Total heterogeneity was moderate with a relatively large amount of heterogeneity observed due to differences within studies (`r fib_i2_null`).

AICc scores included log transformed influent concentration and the aridity index\texttimes BMP subcategory interaction as moderators for the FIB model (Table \@ref(tab:modelaic)).
Moderator terms and interactions explained a high proportion of effect size variance (`r fib_r2`) in the FIB model.
Increased influent concentrations ($\beta$ = 0.25, 95% CI [0.14, 0.37]) resulted in significantly larger ROM effect for FIB (Figure \@ref(fig:fibeffect)).
Compared to the baseline aridity index\texttimes detention BMP subcategory interaction, infiltration ($\beta$ = -29.90, 95% CI [-50.34, -9.47]), livestock management ($\beta$ = -30.37, 95% CI [-50.93, -9.81]), and treatment ($\beta$ = -30.33, 95% CI [-49.62, -11.03]) interactions had significantly smaller slopes.
However, the data had uneven coverage of BMP subcategories across the aridity index. 
Effects for detention BMPs were clustered in humid climates (aridity index > 0.65) and the resulting estimate for the baseline interaction ($\beta$ = 32.63, 95% CI [12.57, 52.69]) may not be reliable.

@@

We identified 13 eligible TN studies and 14 DIN studies and 31 and 44 effect sizes respectively that could be included in the regression model.
Overall effects showed that BMPs resulted in significant mean reductions in TN (ROM = 0.42, 95% CI [0.21, 0.62]; BMP~eff~ = 34.0%, 95% CI [18.7%, 46.4%]; Figure \@ref(fig:overalleffect)) but not in DIN (ROM = 0.64, 95% CI [-0.08, 1.35]; BMP~eff~ = 47.1%, 95% CI [-8.1%, 74.1%]; Figure \@ref(fig:overalleffect)).
Heterogeneity was high for TN with a large proportion of heterogeneity attributed to within study effect (`r tn_i2_null`).
The DIN model had even higher heterogeneity with a larger proportion attributed between studies (`r din_i2_null`).
AICc scores indicated that none of the moderators resulted in substantial improvement over the intercept only model (Table \@ref(tab:modelaic)).

@@

We found 17 TP studies with 37 effect sizes and 9 PO~4~ studies with 21 effect sizes for inclusion in regression models.
There was a significant overall reduction found for TP (ROM = 0.40, 95% CI [0.03, 0.76]; BMP~eff~ = 32.7%, 95% CI [3.4%, 53.2%]) but no evidence of negative or positive effect for PO~4~ (ROM = -0.18, 95% CI [-0.56, 0.19]; BMP~eff~ = -20.1%, 95% CI [-75.3%, 17.7%]). 
For both the TP and PO~4~ models, heterogenity was high, with moderate to high within study variance and low to moderate between study variance (TP: `r tp_i2_null`; PO~4~: `r po4_i2_null`).
The best model for both parameters only included influent as a moderator (Table \@ref(tab:modelaic)).
Moderators explained a relatively small amount of variance for both models (TP: `r tp_r2`, PO~4~: `r po4_r2`).
Influent concentration ($\beta$ = 0.23, 95% CI [-0.035, 0.49]) was not significant at the 95% confidence level for the TP model (Figure \@ref(fig:phoseffect); Table S4).
Influent concentration ($\beta$ = 0.27, 95% CI [0.085, 0.44]) was significant for the PO~4~ model (Figure \@ref(fig:phoseffect); Table S5).

@@

Our systematic review revealed strong spatial disparities in published BMP studies (Figure \@ref(fig:studymap)).
Similar spatial disparities have been identified and discussed in @kochNitrogenRemovalStormwater2014, @grudzinskiDoesRiparianFencing2020 and can be problematic for extrapolating results to other regions of interest.
Inconsistent spatial coverage presents a challenge for disentangling confounding spatially correlated predictors such as climate and soil due to poor representation within the dataset.
@horvathEffectsRegionalClimate2023 found overlapping BMP type and climate groups within their dataset that reduce the ability to distinguish effects due to either BMP type or climate.
Similarly, we found detention type BMPs clustered only in humid climates (high aridity index) which reduces our confidence in extrapolating the interaction between BMP types and aridity index for FIB (Figure \@ref(fig:fibeffect)).
Not only were there spatially disparities, but we observed that the relative distribution of aridity index values does not resemble the distribution of aridity values across the U.S. (Figure \@ref(fig:aiindex)).
Our review indicates that BMP studies are over represented in the generally humid regions of the country and underrepresented the more arid regions.
Study scale, runoff sources and BMP types appeared well distributed, with the caveat that we are not aware of the actual distribution of these values in BMPs deployed across the country.

@@

```{r bmpsummary}
#| fig.cap: "Summary of (A) study scale, (B) dominant runoff source, and (C) BMPs identified in the systematic review."
#| #| fig.pos: "p"
#| out.extra: ""
#| out.width: "100%"

knitr::include_graphics("../figures/bmp_summary.pdf")

@@

```{r bmptemporal}
#| fig.cap: "Number of studies identified in the systematic review summarized by (A) publication date and (B) study length."
#| #| fig.pos: "p"
#| out.extra: ""
#| out.width: "100%"

knitr::include_graphics("../figures/bmp_temporal_summary.pdf")

@@

```{r studymap}
#| fig.cap: "Distribution of studies identified in the systematic review by state and parameter."
#| fig.pos: "p"
#| out.extra: ""
#| out.width: "100%"

knitr::include_graphics("../figures/study_map.pdf")

@@

```{r overalleffect}
#| fig.cap: "Estimated effect sizes and intervals from the intercept only multilevel random effects model. Individual points represent studies, with size scaled by sampling variance. The point estimate with uncertaintity bars indicate the estimated overall effect, 95% confidence intervals, and 95% prediction intervals. Here, \\textit{k} indicates the number of overall effects with the number of unique studies in parenthesis."
#| fig.pos: "p"
#| out.extra: ""
#| out.width: "100%"

knitr::include_graphics("../figures/overall_effect.pdf")
```

```{r fibeffect}
#| fig.cap: "Predicted marignal effect of influent FIB and aridity index (conditioned on BMP subcategory). Solid lines are the predicted mean effect, dashed lines are the 95% confidence intervals, and the dotted lines are the 95% prediction intervals. Individual dots represent each effect size identified in the literature with the size scaled by sampling variance."
#| fig.pos: "p"
#| out.extra: ""
#| out.width: "100%"

knitr::include_graphics("../figures/bac_predicted.pdf")
```

```{r phoseffect}
#| fig.cap: "Predicted marignal effect of influent pollutant concentration on TP (Panel A) and PO\\textsubscript{4} (Panel B) reductions. Solid lines are the predicted mean effect, dashed lines are the 95% confidence intervals, and the dotted lines are the 95% prediction intervals. Individual dots represent each effect size identified in the literature with the size scaled by sampling variance."
#| fig.pos: "p"
#| out.extra: ""
#| out.width: "100%"

knitr::include_graphics("../figures/phos_predicted.pdf")
```

```{r aiindex}
#| fig.cap: "Comparison of the relative distributions (density) of aridity index values across the U.S. against aridity index values for studies in the systematic review."
#| fig.pos: "p"
#| out.extra: ""
#| out.width: "50%"

knitr::include_graphics("../figures/aridity_density.pdf")
```

>>>>

## this sets our default code chunk options
knitr::opts_chunk$set(dev = "ragg_png",
                      echo = FALSE,
                      ## figure chunk options
                      fig.cap = TRUE,
                      fig.width = 6,
                      dpi = 300,
                      fig.process = 
                        function(filename) {
                          new_filename <- stringr::str_remove(string = filename,
                                                              pattern = "-1")
                          fs::file_move(path = filename, new_path = new_filename)
                          ifelse(fs::file_exists(new_filename), new_filename, filename)
                        })

@@

Our systematic review identified a total of 33 studies and 125 effect sizes on FIB, 24 studies and 50 effect sizes on TN, 31 studies and 88 effect sizes for DIN, 31 studies and 61 effect sizes for TP, 17 studies and 36 effect sizes for PO~4~, and 33 studies with 125 effect sizes for TSS. 
The majority of studies were identified as smaller scaled lot or field studies (Figure \@ref(fig:fig1) A).
FIB studies had a roughly equal proportion of large watershed/catchment studies and studies conducted at the community/farm scale or smaller.
We also identified that the majority of studies (all parameters) were conducted on urban or non-agricultural runoff (Figure \@ref(fig:fig1) B).
We did identify a wide variety of BMPs in the review, but it did not appear that any particular type of BMP was responsible for the majority of studies for any given parameter (Figure \@ref(fig:fig1) C).
Our review was restricted to studies published after between 1999 and 2023.
The number of studies published for each parameter were roughly uniformly distributed over time (Figure \@ref(fig:fig2) A) and are not indicative of increases or decreases in the number of published studies.
Study length was strongly skewed for all parameters (Figure \@ref(fig:fig2) B). Median study lengths were 3 (DIN), 2 (FIB), 2.5 (PO~4), 2.5 (TN), 2.5 (TP), and 2 (TSS) years. 
There appears to be a strong clustering of BMP studies in the mid-Atlantic region (North Carolina, Virginia, Maryland) with other states sparsely represented or completely absent from the review (Figure \@ref(fig:fig3)).

@@

There were only 19 studies and 63 FIB effect sizes available to model after removal of studies and effects that only reported BMP~eff~.
The overall mean effect (estimated with the intercept only multilevel random effects model) showed significant mean reductions in FIB (ROM = 0.85, 95% CI [0.36, 1.34]; BMP~eff~ = 57.4%, 95% CI [30.4%, 73.9%]; Figure \@ref(fig:fig4)) resulting from BMPs. 
Total heterogeneity was moderate with a relatively large amount of heterogeneity observed due to differences within studies (`r fib_i2_null`).

AICc scores included log transformed influent concentration and the aridity index\texttimes BMP subcategory interaction as moderators for the FIB model (Table \@ref(tab:modelaic)).
Moderator terms and interactions explained a high proportion of effect size variance (`r fib_r2`) in the FIB model.
Increased influent concentrations ($\beta$ = 0.25, 95% CI [0.14, 0.37]) resulted in significantly larger ROM effect for FIB (Figure \@ref(fig:fig5)).
Compared to the baseline aridity index\texttimes detention BMP subcategory interaction, infiltration ($\beta$ = -29.90, 95% CI [-50.34, -9.47]), livestock management ($\beta$ = -30.37, 95% CI [-50.93, -9.81]), and treatment ($\beta$ = -30.33, 95% CI [-49.62, -11.03]) interactions had significantly smaller slopes.
However, the data had uneven coverage of BMP subcategories across the aridity index. 
Effects for detention BMPs were clustered in humid climates (aridity index > 0.65) and the resulting estimate for the baseline interaction ($\beta$ = 32.63, 95% CI [12.57, 52.69]) may not be reliable.

@@

We identified 13 eligible TN studies and 14 DIN studies and 31 and 44 effect sizes respectively that could be included in the regression model.
Overall effects showed that BMPs resulted in significant mean reductions in TN (ROM = 0.42, 95% CI [0.21, 0.62]; BMP~eff~ = 34.0%, 95% CI [18.7%, 46.4%]; Figure \@ref(fig:fig4)) but not in DIN (ROM = 0.64, 95% CI [-0.08, 1.35]; BMP~eff~ = 47.1%, 95% CI [-8.1%, 74.1%]; Figure \@ref(fig:fig4)).
Heterogeneity was high for TN with a large proportion of heterogeneity attributed to within study effect (`r tn_i2_null`).
The DIN model had even higher heterogeneity with a larger proportion attributed between studies (`r din_i2_null`).
AICc scores indicated that none of the moderators resulted in substantial improvement over the intercept only model (Table \@ref(tab:modelaic)).

@@

We found 17 TP studies with 37 effect sizes and 9 PO~4~ studies with 21 effect sizes for inclusion in regression models.
There was a significant overall reduction found for TP (ROM = 0.40, 95% CI [0.03, 0.76]; BMP~eff~ = 32.7%, 95% CI [3.4%, 53.2%]) but no evidence of negative or positive effect for PO~4~ (ROM = -0.18, 95% CI [-0.56, 0.19]; BMP~eff~ = -20.1%, 95% CI [-75.3%, 17.7%]). 
For both the TP and PO~4~ models, heterogenity was high, with moderate to high within study variance and low to moderate between study variance (TP: `r tp_i2_null`; PO~4~: `r po4_i2_null`).
The best model for both parameters only included influent as a moderator (Table \@ref(tab:modelaic)).
Moderators explained a relatively small amount of variance for both models (TP: `r tp_r2`, PO~4~: `r po4_r2`).
Influent concentration ($\beta$ = 0.23, 95% CI [-0.035, 0.49]) was not significant at the 95% confidence level for the TP model (Figure \@ref(fig:fig6); Table S4).
Influent concentration ($\beta$ = 0.27, 95% CI [0.085, 0.44]) was significant for the PO~4~ model (Figure \@ref(fig:fig6); Table S5).

@@

Our systematic review revealed strong spatial disparities in published BMP studies (Figure \@ref(fig:fig3)).
Similar spatial disparities have been identified and discussed in @kochNitrogenRemovalStormwater2014, @grudzinskiDoesRiparianFencing2020 and can be problematic for extrapolating results to other regions of interest.
Inconsistent spatial coverage presents a challenge for disentangling confounding spatially correlated predictors such as climate and soil due to poor representation within the dataset.
@horvathEffectsRegionalClimate2023 found overlapping BMP type and climate groups within their dataset that reduce the ability to distinguish effects due to either BMP type or climate.
Similarly, we found detention type BMPs clustered only in humid climates (high aridity index) which reduces our confidence in extrapolating the interaction between BMP types and aridity index for FIB (Figure \@ref(fig:fig5)).
Not only were there spatially disparities, but we observed that the relative distribution of aridity index values does not resemble the distribution of aridity values across the U.S. (Figure \@ref(fig:fig7)).
Our review indicates that BMP studies are over represented in the generally humid regions of the country and underrepresented the more arid regions.
Study scale, runoff sources and BMP types appeared well distributed, with the caveat that we are not aware of the actual distribution of these values in BMPs deployed across the country.

@@

```{r fig1}
#| fig.cap: "Summary of (A) study scale, (B) dominant runoff source, and (C) BMPs identified in the systematic review."
#| #| fig.pos: "p"
#| out.extra: ""
#| out.width: "100%"

knitr::include_graphics("frontiers_submission_files/figure-latex/fig1.pdf")

@@

```{r fig2}
#| fig.cap: "Number of studies identified in the systematic review summarized by (A) publication date and (B) study length."
#| #| fig.pos: "p"
#| out.extra: ""
#| out.width: "100%"

knitr::include_graphics("frontiers_submission_files/figure-latex/fig2.pdf")

@@

```{r fig3}
#| fig.cap: "Distribution of studies identified in the systematic review by state and parameter."
#| fig.pos: "p"
#| out.extra: ""
#| out.width: "100%"

knitr::include_graphics("frontiers_submission_files/figure-latex/fig3.pdf")

@@

```{r fig4}
#| fig.cap: "Estimated effect sizes and intervals from the intercept only multilevel random effects model. Individual points represent studies, with size scaled by sampling variance. The point estimate with uncertaintity bars indicate the estimated overall effect, 95% confidence intervals, and 95% prediction intervals. Here, \\textit{k} indicates the number of overall effects with the number of unique studies in parenthesis."
#| fig.pos: "p"
#| out.extra: ""
#| out.width: "100%"

knitr::include_graphics("frontiers_submission_files/figure-latex/fig4.pdf")
```

```{r fig5}
#| fig.cap: "Predicted marignal effect of influent FIB and aridity index (conditioned on BMP subcategory). Solid lines are the predicted mean effect, dashed lines are the 95% confidence intervals, and the dotted lines are the 95% prediction intervals. Individual dots represent each effect size identified in the literature with the size scaled by sampling variance."
#| fig.pos: "p"
#| out.extra: ""
#| out.width: "100%"

knitr::include_graphics("frontiers_submission_files/figure-latex/fig5.pdf")
```

```{r fig6}
#| fig.cap: "Predicted marignal effect of influent pollutant concentration on TP (Panel A) and PO\\textsubscript{4} (Panel B) reductions. Solid lines are the predicted mean effect, dashed lines are the 95% confidence intervals, and the dotted lines are the 95% prediction intervals. Individual dots represent each effect size identified in the literature with the size scaled by sampling variance."
#| fig.pos: "p"
#| out.extra: ""
#| out.width: "100%"

knitr::include_graphics("frontiers_submission_files/figure-latex/fig6.pdf")
```

```{r fig7}
#| fig.cap: "Comparison of the relative distributions (density) of aridity index values across the U.S. against aridity index values for studies in the systematic review."
#| fig.pos: "p"
#| out.extra: ""
#| out.width: "50%"

knitr::include_graphics("frontiers_submission_files/figure-latex/fig7.pdf")
```
